---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->
#

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```



## pretty Representations of oligo-nucleotides

The **pRon** package contains functions to help handle oligo-nucleotides (k-mers), including creating frequency/energy profile figures.

### Summary

This package provides some useful functions that I frequently used:

 * quick summary of large objects in memory
 * ruler style axis for plots
 * nicer (and more convinient) heatmap
 * smearing and running mean functions for fast smoothing



### Installation

```{r, eval=FALSE}
devtools::install_bitbucket(repo="markheron/pRon", auth_user="user_name", password="your_password")
```

or install all of Marks packages with the **maRs** package:

```{r, eval=FALSE}
install_marks_package_suite(auth_user="user_name")
```



### Usage

```{r, echo=TRUE}
library(pRon)

oligo_names(2)
```

```{r, eval=FALSE, echo=TRUE}

fastas <- cut_out_fasta_multiple(chr=chr_vec, pos = pos_vec, strand = strand_vec, size = 100, order = 2, genome_dir = "path/to/genome")
num_fasta_matrix <- fasta2num(fastas=fastas, oligo_length = 2)
plotOligoFreqs(num_fasta_matrix)
```


### License

The **pRon** package is licensed under the GPLv3 (http://www.gnu.org/licenses/gpl.html).
